---
title: "Dean's Dilemma Case Study"
author: "Prince Barai"
date: "February 3, 2018"
output: html_document
---

# 1. Set the working directory.
```{r}
setwd("C:/Users/prince_pratik7/Desktop/Machine Learning/Data Analytics/Data Visualisation/Day 6")
```
# 2. Read the dataset using the read.csv() function.
```{r}
dilemna <- read.csv(paste("Data - Deans Dilemma.csv" , sep = ""))
```
# 3. Use the View() function to view the dataframe created in the previous step.
```{r}
View(dilemna)
```
# 4. Describing the Dataset
```{r}
library(psych)
describe(dilemna)
```
# 5. Calculate the median salary of all the students in the dataset.
```{r}
median(dilemna$Salary , na.rm = FALSE)
```
# 6. Calculate the percentage of students who were placed upto 2 decimal places.
```{r}
percent <- length(dilemna$Placement[dilemna$Placement == "Placed"]) / length(dilemna$Placement) * 100
options(digits = 4)
percent
```
# 7. Create a dataframe called "placed", that contains a subset of only those students who were successfully placed.
```{r}
placed <- subset(dilemna , Placement == "Placed" , select = c(Percent_MBA , Gender , Salary))
placed
```
# 8. Calculate median salary of students who were placed.
```{r}
median(dilemna$Salary[dilemna$Placement == "Placed"] , na.rm = FALSE)
```
# 9.  Create a table showing the mean salary of males and females, who were placed
```{r}
agg.data <- aggregate(Salary ~ Gender + Placement , data = dilemna , mean)
agg.data
```
# 10. Generate a histogram showing a breakup of MBA performance of the students who were placed.
```{r}
hist(placed$Percent_MBA , main = "MBA Performance of placed students" , xlab = "MBA Percentage" , ylab = "Count" , xlim = c(50,80) , ylim = c(0,150) , col = "grey" , breaks = c(50,seq(60,80,10)))

```
# 11. Create a dataframe called "notplaced", that contains a subset of only those students who were not placed after their MBA.
```{r}
notplaced <- subset(dilemna , Placement == "Not Placed" , select = c(Percent_MBA , Gender , Salary))
notplaced
```
# 12. Draw two histograms side-by-side, visually comparing the MBA performance of Placed and Not Placed students.

```{r}
par(mfrow = c(1,2))

hist(placed$Percent_MBA , main = "MBA Performance of placed students" , xlab = "MBA Percentage" , ylab = "Count" , xlim = c(50,80) , ylim = c(0,150) , col = "grey" , breaks = c(50,seq(60,80,10)))

hist(notplaced$Percent_MBA , main = "MBA Performance of not placed students" , xlab = "MBA Percentage" , ylab = "Count" , xlim = c(50,80) , ylim = c(0,40) , col = "grey" , breaks = c(50,seq(60,80,10)))
```

```{r}
par(mfrow = c(1,1))
```
# 13. Draw two boxplots, one below the other, comparing the distribution of salaries of males and females who were placed.
```{r}
library(lattice)
bwplot(Gender ~ Salary , data = placed , horizontal = TRUE , xlab = "Salary" , ylab = "Gender" , main = "Comparison of Salaries of Males and Females")
```
# 14. Create a dataframe called placedET, representing students who were placed after the MBA and who also gave some MBA entrance test before admission into the MBA program.
```{r}
placedET <- subset(dilemna , Placement == "Placed" & S.TEST == 1 , select = c(Salary , Percent_MBA , Percentile_ET))
placedET
```
# 15. Draw a Scatter Plot Matrix for 3 variables - {Salary, Percent_MBA, Percentile_ET} using the dataframe placedET.
```{r}
library(psych)
library(car)
scatterplotMatrix(formula = ~ Salary + Percent_MBA + Percentile_ET, data = placedET)
```






