---
title: "Dean's Dilemma(Part-II)"
author: "Prince Barai"
date: "February 5, 2018"
output: html_document
---

# Synopsis
This assignment is based on the case study of Dean's Dilemma and it is in 6 parts:

1.Submit your R code that creates a table showing the mean salary of males and females, who were placed.
2.What is the average salary of male MBAs who were placed?
3.What is the average salary of female MBAs who were placed?
4.Submit R code to run a t-test for the Hypothesis "The average salary of the male MBAs is higher than the average salary of female MBAs."
5.What is the p-value based on the t-test?
6.Please interpret the meaning of the t-test, as applied to the average salaries of male and female MBAs.

#Read the data set into RStudio
```{r}
deansdilemma.df <- read.csv(paste("Data - Deans Dilemma.csv", sep=""))
View(deansdilemma.df)
```
# Use R to create a dataframe called placed, that contains a subset of only those students who were successfully placed.
```{r}
placed.df<-deansdilemma.df[which(deansdilemma.df$Placement_B==1),]
View(placed.df)
```
# Submit your R code that creates a table showing the mean salary of males and females, who were placed.
```{r}
aggregate(placed.df$Salary, by=list(Gender=placed.df$Gender),mean)
```
# What is the average salary of male MBAs who were placed?
```{r}
male.df<-placed.df[which(placed.df$Gender.B==0),]
View(male.df)
mean(male.df$Salary)
```
# What is the average salary of female MBAs who were placed?
```{r}
female.df<-placed.df[which(placed.df$Gender.B==1),]
View(female.df)
mean(female.df$Salary)
```
# Submit R code to run a t-test for the Hypothesis "The average salary of the male MBAs is higher than the average salary of female MBAs."
```{r}
aggregate(placed.df$Salary, by=list(placed.df$Gender), FUN=mean)
```
# T-Test
```{r}
t.test(Salary ~ Gender, data=placed.df)
```

# What is the p-value based on the t-test?
the p-value based on the t-test is 0.00234.

# Please interpret the meaning of the t-test, as applied to the average salaries of male and female MBAs.
Based on the above output of the t-test, we can not reject the hypothesis that "The average salary of the male MBAs is higher than the average salary of female MBAs." (p>0.001)

