---
title: "Titanic Case (Part-II)"
author: "Prince Barai"
date: "February 5, 2018"
output: html_document
---
# Synopsis
This assignment is based on the case study of Titanic and it is divided in 3 parts:

# Recall the Titanic Data.csv data associated with the "Sinking of the RMS Titanic" that you analyzed on WEEK 1, DAY 5
```{r}
titanic.df <- read.csv(paste("Titanic Data.csv", sep=""))
View(titanic.df)
```
#Use R to create a table showing the average age of the survivors and the average age of the people who died.
```{r}
aggregate(titanic.df$Age, by=list(Survived=titanic.df$Survived),mean)
```
# Use R to run a t-test to test the following hypothesis:
# H2: The Titanic survivors were younger than the passengers who died.
t.test(Age ~ Survived, data=titanic.df)
```{r}
t.test(Age ~ Survived, data=titanic.df)
```
#Result of Independent t-test
Based on the above output of the t-test, we can not reject the hypothesis that The Titanic survivors were younger than the passengers who died. (p>0.001)