---
title: "Titanic"
author: "Prince Barai"
date: "February 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Task 2B: Reading the DataSet
fjdfndkfn
```{r}
titanic<-read.csv("Titanic Data.csv")
head(titanic)
```
# Task 3A: Use R to Count the total numbe of passengers on board the Titanic
```{r}
nrow(titanic)
```
Total Number of Passengers : 889
#Task 3B : Use R to Count the number of passengers who survived the sinking of the Titanic.
```{r}
mytable <- with(titanic,table(Survived))
addmargins(mytable)
```
Total Number of Passengers Survived: 340
# Task 3C : Use R to measure the percentage of passengers who survived the sinking of the Titanic.
```{r}
prop.table(mytable)*100
```
Percentage of Passengers Survived: 38.24522 %
#Task 3D : Use R to count the number of first-class passengers who survived the sinking of the Titanic.
```{r}
mytable1<- xtabs(~Survived+Pclass , data=titanic)
addmargins(mytable1)
```
Conclusion: 134 out of 214 first class passengers survived.

#Task 3E : Use R to measure the percentage of first-class passengers who survived the sinking of the Titanic.
```{r}
prop.table(mytable1,2)*100
```
Conclusion: Percentage of First Class Passenger Survived = 62.61682% 

#Task 3F : Use R to count the number of females from First-Class who survived the sinking of the Titanic
```{r}
mytable2 <- xtabs(~Pclass+Sex+Survived , data=titanic)
mytable2
```
Conclusion: 89 Females of First Class Survived the Sinking of the Titanic

#Task 3G : Use R to measure the percentage of survivors who were female
```{r}
mytable3 <- xtabs(~Sex+Survived , data=titanic)
prop.table(mytable3,2)*100
```
Conclusion: Female Survivors in terms of Percentage = 67.94118 %

# Task 3H : Use R to measure the percentage of females on board the Titanic who survived
```{r}
prop.table(mytable3,1)*100
```
Conclusion: Females on board the Titanic survived = 74.03846%

# Task 3I : Run a Pearson's Chi-squared test to test the following hypothesis:
Hypothesis: "The proportion of females onboard who survived the sinking of the Titanic was higher than the proportion of males onboard who survived the sinking of the Titanic."
```{r}
chisq.test(mytable3)
```
Conclusion: The p-values are the probability of obtaining the sampled results, assuming independence of the row and column variables in the population. Since the probability is small (p < 0.01), we reject the Null hypothesis that survival of passenger and sex of passenger are independent.

Thus it suggests that whether a passenger will survive or not, depends on the sex of the passenger(male or female).

