---
title: "Analysis of Hotel Prices In India"


author: "Prince Barai"


date: "February 22, 2018"
output: html_document
---
<b> Analysis of Hotel Prices


NAME: Prince Barai


EMAIL: princepratik7284@gmail.com


COLLEGE : University of Engineering & Management, Kolkata </b>



<b>Setup The Working Directory and Make Sure This Package Are Already Installed</b>


```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(corrgram)
library(gridExtra) 
library(vcd)
library(psych)
library(car)
library(corrplot)
```

<b> Functions </b>

```{r}
detect_outliers <- function(inp, na.rm=TRUE) {
  i.qnt <- quantile(inp, probs=c(.25, .75), na.rm=na.rm)
  i.max <- 1.5 * IQR(inp, na.rm=na.rm)
  otp <- inp
  otp[inp < (i.qnt[1] - i.max)] <- NA
  otp[inp > (i.qnt[2] + i.max)] <- NA
  #inp <- count(inp[is.na(otp)])
  sum(is.na(otp))
}

Non_outliers <- function(x, na.rm = TRUE, ...) {
  qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
  H <- 1.5 * IQR(x, na.rm = na.rm)
  y <- x
  y[x < (qnt[1] - H)] <- NA
  y[x > (qnt[2] + H)] <- NA
  y
}

Remove_Outliers <- function ( z, na.rm = TRUE){
 Out <- Non_outliers(z)
 Out <-as.data.frame (Out)
 z <- Out$Out[match(z, Out$Out)]
 z
}

Graph_Boxplot <- function (input, na.rm = TRUE){
Plot <- ggplot(dfrModel, aes(x="", y=input)) +
            geom_boxplot(aes(fill=input), color="green") +
            labs(title="Outliers")
Plot
}
```


<b> Reading The DataSet </b>


```{r}
dfrModel <- read.csv("./Cities42.csv", header=T, stringsAsFactors=F)
```

<b> Visualizing The Length And Breadth of Dataset </b>



```{r}
View(dfrModel)
dim(dfrModel)
```



```{r}
intRowCount <- nrow(dfrModel)
head(dfrModel)
```

Observation I: 

There are total 'intRowCount' data records in the file.
As there are Non Numeric data as well in the given dataset, so we are going to remove the non numeric data.

<b> Data Cleaning </b>



```{r}

dfrModel <- select(dfrModel, -c(CityName, Date, HotelName, HotelAddress, HotelDescription, HotelPincode ))
```

<b> Summary </b>


```{r}
describe(dfrModel$Population)[,c(2,3,4,5,8,9)]
```


```{r}
describe(dfrModel$StarRating)[,c(2,3,4,5,8,9)]
```

```{r}
describe(dfrModel$StarRating)[,c(2,3,4,5,8,9)]
```


```{r}
describe(dfrModel$HotelCapacity)[,c(2,3,4,5,8,9)]
```

<b> Observations </b>

Dependent Variable is
Y = Hotel Rent

Independent Variable is
X1 = Star Rating
X2 = IsTouristDestination
X3 = Airport Distance
X4 = Hotel Capacity

<b> Creating Two Way Contigency Table </b>



```{r}
aggregate(dfrModel$RoomRent, by=list(weekend = dfrModel$IsWeekend, newyearseve = dfrModel$IsNewYearEve), mean)
```


```{r}
aggregate(dfrModel$RoomRent, by=list(Metrocity = dfrModel$IsMetroCity, TouristPlace = dfrModel$IsTouristDestination), mean)
```


```{r}
aggregate(dfrModel$RoomRent, by=list(freewifi = dfrModel$FreeWifi, freeBreakfast = dfrModel$FreeBreakfast, swimmingPool = dfrModel$HasSwimmingPool), mean)
```

<b> Box Plot </b>


```{r}
Graph_Boxplot(dfrModel$StarRating)
```


```{r}
Graph_Boxplot(dfrModel$Airport)
```

```{r}
Graph_Boxplot(dfrModel$HotelCapacity)
```

<b> Observations: </b>


There are few outliers in the datasets

<b> Drawing Coxplot and Comparing  </b>


```{r}
boxplot(dfrModel$RoomRent ~ dfrModel$IsWeekend, xlab = "Weekend" , ylab = "Room Rent" , main = "Comparison of Room rent over weekend or weekdays", ylim = c(0,30000), col = "skyblue")
```


<b> Drawing Histogram </b>


```{r}
hist(dfrModel$StarRating, main = "Star Rating Distribution", xlab = "Stars")
```


```{r}
hist(dfrModel$Airport, main = "Distrubtion of distance to the nearest major airport", xlab = "Dist to the nearest major Airport in km")
```

<b> Tables </b>


```{r}
TouristDestination <- table(dfrModel$IsTouristDestination)
TouristDestination
```


```{r}
prop.table(TouristDestination)
```

<b> Observations </b>

Here

1 Implies Tourist Destination
0 Implies Not an tourist destination

<b> Scatter Plot </b>


```{r}
plot(y=dfrModel$RoomRent, x=dfrModel$Airport,
     col="green",
     ylim=c(0, 350000), xlim=c(0, 150), 
     main="Relationship Btw Room Rent and Airport Distance",
     ylab="Hotel Rent", xlab="Airport Distance")
```


```{r}
scatterplot(dfrModel$Airport, dfrModel$RoomRent , main="Relationship Btw Room Rent and Airport Distance", xlab="Airport Distance", ylab="Hotel Rent")
```


```{r}

plot((dfrModel$IsTouristDestination),jitter(dfrModel$RoomRent),
     col="green",
     ylim=c(0, 350000), xlim=c(0, 5), 
     main="Relationship Btw Room Rent and Tourist Destination",
     ylab="Hotel Rent", xlab="Tourist Destination")
```

```{r}
plot(y=dfrModel$RoomRent, x=dfrModel$StarRating,
     col="blue",
     ylim=c(0, 350000), xlim=c(0, 10), 
     main="Relationship Btw Room Rent and Star Rating of Hotel",
     ylab="Hotel Rent", xlab="Star Rating")
```


```{r}
plot(y=dfrModel$RoomRent, x=dfrModel$HotelCapacity,
     col="green",
     ylim=c(0, 350000), xlim=c(0, 150), 
     main="Relationship Btw Room Rent and Hotel Capacity",
     ylab="Hotel Rent", xlab="Hotel Capacity")
```


```{r}
scatterplot(dfrModel$HotelCapacity, dfrModel$RoomRent , main="Relationship Btw Room Rent and Hotel Capacity", xlab="Hotel Capacity", ylab="Hotel Rent")
```

<b> Observations </b>


1.Above scatter plot is showing some relationship between Hotel rent and other Independent variables.

<b> Scatter Plot </b>


```{r}
corrplot(corr=cor(dfrModel[ , c(4,7,8,9,12)], use="complete.obs"), 
         method ="ellipse")
```

<b> Correlation </b>


```{r}
cor(dfrModel[, c(4,7,8,9,12)]) 
```

<b> T-Test </b>
 
```{r}
t.test(dfrModel$RoomRent ~ dfrModel$IsNewYearEve)
```

From t-test that the P-Value = 3.046e-05 (<0.05) Which is small enough for Rejecting the Null Hupothesis.
Hence there is impact on the room rents on New Year's eve and on other days.


<b> Summary </b>


Data has been loaded successfully


Data has been summarized to know the different statistical values
Outliers has been find out in each variable and Evry variable is plotted on Box plot to know about the outliers
Dependent and Independent variable are find out.
Dependent Variable is
Y = Hotel Rent


Independent Variable is


X1 = Star Rating


X2 = IsTouristDestination


X3 = Airport Distance


X4 Can also be Hotel Capacity

<b> Scatter plot as well as Corrgram is plotted which is showing the relationship between salaries and other variables
Continuous variable are shown on Box plot while tables is used for discrete variables.  </b>

