---
title: "SixAirlinesData"
author: "Prince Barai"
date: "February 16, 2018"
output: html_document
---

# Premium Economy Vs Economy Ticket Pricing by Airlines

Premium Economy is found mostly on international flights and, compared to standard Economy, offers about 5-7 inches of extra legroom as well as additional amenities, which can include: 1-2 extra inches of seat width. 2-3 extra inches of seat recline. Adjustable headrests, legrests, or lumbar support.

# RESEARCH QUESTION: What factors explain the difference in price between an economy ticket and a premium-economy airline ticket?

```{r}
airlines.df <- read.csv(paste("SixAirlinesDataV2.csv", sep=""))
View(airlines.df)
```

Summarize the data to understand the mean, median, standard deviation of each variable

```{r}
library(psych)
summary(airlines.df)
```

As we see from the above, we make the following observations:

Airline Data is of 6 main row types with British Airways occupying the maximum entries.

Boeing Aircraft is comes up more than Airbus in the Data.

Flight Duration is averaged around 7.57 Hrs with minimum flight of 1 hr 2 mins and maximum time of 14 Hours & 6 mins

The Price of Premium seats range around $1737.

The Price of Economy Seats are lower, ranging around $1327.


```{r}
aggregate(list(PercentPremium=airlines.df$PercentPremiumSeats),list(name=airlines.df$Airline),FUN=mean)
```
So, as we see from the above Data, the percentage of Premium Seats are around 10-18 % of the total seats.

# Draw Box Plots / Bar Plots to visualize the distribution of each variable independently


```{r}
Economy<-aggregate(airlines.df$SeatsEconomy,list(airlines.df$Airline),mean)
Premium<-aggregate(airlines.df$SeatsPremium,list(airlines.df$Airline),mean)
Economy
```

Premium

```{r}
Premium
```


# Draw Scatter Plots to understand how are the variables correlated pair-wise

```{r}
plot(airlines.df$Airline,airlines.df$SeatsPremium,col="purple",main="Airline vs Economy Seats",ylab="Mean Economy Seats")

```



```{r}
plot(airlines.df$Airline,airlines.df$SeatsEconomy,col='light blue',main="Airline vs Premium Seats",ylab="Mean PremiumSeats")
```


# Correlation between Variables

```{r}
correlation_01 <-cor(airlines.df[,6:18])
correlation_01[,7:8]
```


We can see that there are various Correlations among all rows and Price of Economy and Price Of Premium Seats.

# Draw a Corrgram; Create a Variance-Covariance Matrix


```{r}
corr_01<-airlines.df[,3]+airlines.df[,6:14]
corrr<-round(cor(corr_01),2)
corrr
```


```{r}
library(corrplot)
```


```{r}
corrplot(corrr, method = "square")
```


From the above corrplot, we figure that the difference in price for a premium ticket and a economy ticket is mainly due to various airlines offering these seats


# T-Test

There is no effect of Airline on Price of Premium Seats and Economy Seats.

```{r}
myt<-table(airlines.df$PriceEconomy)
myp<-table(airlines.df$PricePremium)
myx<-table(airlines.df$Airline)
t.test(myp,myx)
```


```{r}
t.test(myt,myx)
```


Since the value of p is < 0.05, we can reject our null hypothesis that airlines do not play a significant role in pricing

# Regression Analysis


```{r}
Model1=PricePremium~SeatsEconomy+FlightDuration+SeatsPremium+PitchEconomy+PitchPremium+WidthEconomy+WidthPremium+PriceEconomy+PriceRelative+SeatsTotal+PitchDifference+WidthDifference+PercentPremiumSeats

fit<-lm(Model1,data=airlines.df)
summary(fit)
```



```{r}
Model2=PriceEconomy~SeatsEconomy+FlightDuration+SeatsPremium+PitchEconomy+PitchPremium+WidthEconomy+WidthPremium+PricePremium+PriceRelative+SeatsTotal+PitchDifference+WidthDifference+PercentPremiumSeats

fit1<-lm(Model2,data=airlines.df)
summary(fit)
```



We test for all Numeric values and on the basis of above information of Regression Analysis on both PricePremium and PriceEconomic, we infer that:

SeatsEconomy , SeatsPremium ,PitchEconomy ,PitchPremium ,WidthEconomy ,PriceEconomy ,PriceRelative ,PercentPremiumSeats are highly significant Independent Variables.

They are all highly significant and highly correlated to Price of the Seats. FlightDuration ,WidthPremium ,SeatsTotal, PitchDifference, WidthDifference are not significant at all having p>0.05

# Other Observations:

Residual Standard Error is 300.6 on 447 x-values. The model accounts for 94.67% of variance in the data. The Actual R-Squared Value is 94.55% as penalty is imposed for more than one x-value. F-STatistics check whether the predictor variables taken together, predict the response variable above chance levels.Here,F-Statistic are 794.5 on 10 implying high correlation among 10 x-vales and y. This shows us that this is a good model since the p-value is pretty low(2.2e-16) implying high correlation.