---
title: "Store24"
author: "Prince Barai"
date: "February 13, 2018"
output: html_document
---
# Store24 (A): Managing Employee Retention

TASK 4c - Download and review the "Store24.csv" data file associated with this case. Using R, read the data into a data frame called store.Using R, get the summary statistics of the data.Confirm that the summary statistics generated from R are consistent with Exhibit 3 from the Case.

```{r}
setwd("C:/Users/prince_pratik7/Desktop/Machine Learning/Data Analytics/Data Visualisation/Week 3 Day 1")
```


# Reading the DataSet in R
```{r}
store.df <-read.csv(paste ("Store24.csv", sep=""))
```

# Summary of Dastaset
```{r}
summary(store.df)
```

TASK 4d -

1. Use R to measure the mean and standard deviation of Profit.

```{r}
mean(store.df$Profit)
```

```{r}
sd(store.df$Profit)
```

Mean = 276313.6 Standard Deviation = 89404.08

2. Use R to measure the mean and standard deviation of MTenure.

```{r}
mean(store.df$MTenure)
```

Mean = 45.29644 Standard Deviation = 57.67155

3. Use R to measure the mean and standard deviation of CTenure.

```{r}
mean(store.df$CTenure)
```


```{r}
sd(store.df$CTenure)
```

Mean = 13.9315 Standard Deviation = 17.69752

# Task 4e - Sorting and Subsetting data in R

```{r}
attach(mtcars)
View(mtcars)
newdata <- mtcars[order(mpg),] # sort by mpg (ascending)
View(newdata)
newdata[1:5,]
```


```{r}
newdata <- mtcars[order(-mpg),] # sort by mpg (descending)
View(newdata)
detach(mtcars)
```

# TASK 4f- Replicate Exhibit 1 shown in the case, using R :

4. Use R to print the {StoreID, Sales, Profit, MTenure, CTenure} of the top 10 most profitable stores.

```{r}
attach(store.df)
newdata <- store.df[order(-Profit),]
View(newdata)
newdata[1:10,c("store","Sales","Profit","MTenure","CTenure")]
```

5. Use R to print the {StoreID, Sales, Profit, MTenure, CTenure} of the bottom 10 least profitable stores.

```{r}
attach(store.df)
```

```{r}
newdata <- store.df[order(Profit),]
View(newdata)
newdata[10:1,c("store","Sales","Profit","MTenure","CTenure")]
```

# TASK 4g - Scatter Plots

6. Use R to draw a scatter plot of Profit vs. MTenure.

```{r}
library(car)
scatterplot(store.df$Profit~store.df$MTenure , xlab="MTenure", ylab="Profit", main="Profit Vs. MTenure", , labels=row.names(store.df))
```

# TASK 4h - Scatter Plots (contd.)

7. Use R to draw a scatter plot of Profit vs. CTenure.

```{r}
scatterplot(store.df$Profit~store.df$CTenure , xlab="CTenure", ylab="Profit", main="Profit Vs. CTenure", , labels=row.names(store.df))
```

# TASK 4i - Correlation Matrix

8. Use R to construct a Correlation Matrix for all the variables in the dataset. (Display the numbers up to 2 Decimal places)

```{r}
cor <- cor(store.df)
round(cor,2)
```


# TASK 4j - Correlations

9. Use R to measure the correlation between Profit and MTenure. (Display the numbers up to 2 Decimal places)

```{r}
round(cor(Profit,MTenure),2)
```

10. Use R to measure the correlation between Profit and CTenure. (Display the numbers up to 2 Decimal places)

```{r}
round(cor(Profit,CTenure),2)
```

# TASK 4k

11. Use R to construct the following Corrgram based on all variables in the dataset.

```{r}
library(corrgram)

corrgram(store.df, lower.panel=panel.shade,upper.panel=panel.pie, text.panel=panel.txt,main="Corrgram of Store Variables")
```

# TASK 4l - Pearson's Correlation Tests

12. Run a Pearson's Correlation test on the correlation between Profit and MTenure. What is the p-value?

```{r}
cor.test(store.df$Profit,store.df$MTenure)
```

The p-value is = 8.193e-05

13.Run a Pearson's Correlation test on the correlation between Profit and CTenure. What is the p-value?

```{r}
cor.test(store.df$Profit,store.df$CTenure)
```

The p-value is = 0.02562

# TASK 4m - Regression Analysis

14. Run a regression of Profit on {MTenure, CTenure Comp, Pop, PedCount, Res, Hours24, Visibility}.

```{r}
profit <- lm(Profit ~ MTenure + CTenure + Comp + Pop + PedCount + Res + Hours24 + Visibility, data = store.df)
summary(profit)
```


TASK 4n
Based on TASK 4m, answer the following questions:

15. List the explanatory variable(s) whose beta-coefficients are statistically significant (p < 0.05).

MTenure (9.72e-08), CTenure (0.028400), Comp (1.94e-05), Pop (0.014890), PedCount (0.000366), Res (0.022623), Hours24 (0.001994).

16. List the explanatory variable(s) whose beta-coefficients are not statistically significant(p > 0.05).
Visibility (0.169411)

# TASK 4o

17. What is expected change in the Profit at a store, if the Manager's tenure i.e. number of months of experience with Store24, increases by one month?

```{r}
profit$coefficients[2]
```

18. What is expected change in the Profit at a store, if the Crew's tenure i.e. number of months of experience with Store24, increases by one month?

```{r}
profit$coefficients[3]
```

# TASK 4p - "Executive Summary"

1. The given data set of store24 has 75 observations and 14 variables.

2. The maximun profit of a given stores is 518998 and the least profit is 122180. From the above analysis, we can say that the 10 most profitable stores have higher manager tenures and crew tenures than the 10 least profitable stores.

3. The correlation between profit and sales is the maximum. (Corrgram) Other variables like ManagerTenure, CrewTenure also affect the profit which we can see by conducting the correlations test.

4. In the Regression test, the p-value of the F-statistic is < 0.05 significantly, which means it is suitable for deriving decisions from the data. The visibility factor has a beta-coefficient > 0.05 and is not very significant statistically.

5. By regression, there's a very high relationship of MTenure and pedcount with profit, a negative relationship between profits and competitors and a good relationship between profits and hours,CTenure,population and residence. So, to maximise profit of the store, one must focus on increasing/decreasing those factors/variables that help increase/decrease the profit of the store.